Sequoidal Categories and Transfinite Games: Towards a Coalgebraic Approach to Linear Logic\footnote{This work was partially supported by [TODO: find the appropriate grant codes]}

### 2017-03-29 round-corner/paper/lipics-v2016-authors/sequoidal.tex
More changes

% Author macros and packages
\usepackage{IEEEtrantools} % for \IEEEeqnarray
\usepackage{pbox} % for \pbox
\usepackage{cmll} % Linear logic symbols!
\usepackage{wasysym} % For left and rigth moons
\usepackage{mathtools}

@@

\begin{theorem}
  If $A,B$ are games, let $J$ be the inclusion functor $\G_s\to\G$ and let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
  \[
    (\G,\G_s,J,\wk)
    \]
  is an inclusive, Cartesian, decomposable, distributive sequoidal closed category.
\end{theorem}

@@

\begin{proposition}
  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right) = \oc A \xrightarrow{\mu_A} \oc A \tensor \oc A$
\end{proposition}
\begin{proof}
  By the (standard) construction of the functor $\CCom(\oc)$, the comultiplication in $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ is given by the composite
  \[
    \begin{tikzcd}
      \oc A \arrow[r, "\oc\Delta"]
        & \oc (A\times A) \arrow[r, "\int_{A,A}\inv"]
          & \oc A \tensor \oc A
    \end{tikzcd}
    \]
\end{proof}

@@

\begin{theorem}
  \label{Coalgebra__CoCoCo}
  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.  Let $A$ be an object of $\C$ (equivalently, of $\C_s$).  Then $\oc A$ is the carrier for the cofree commutative comonoid over $A$.
\end{theorem}

@@

\bibliography{../../../common/phd_bibliography}

>>>>

% Additional packages and macros
\usepackage{IEEEtrantools} % for \IEEEeqnarray
\usepackage{pbox} % for \pbox
\usepackage{cmll} % Linear logic symbols!
\usepackage{wasysym} % For left and rigth moons
\usepackage{mathtools}

@@

\begin{theorem}
  Let $J$ be the inclusion functor $\G_s\to\G$.  If $A,B$ are games, let $\wk_{A,B}\from A\tensor B\to A\sequoid B$ be the natural copycat strategy.  Then
  \[
    (\G,\G_s,J,\wk)
    \]
  is an inclusive, Cartesian, decomposable, distributive sequoidal closed category.
\end{theorem}

@@

\begin{proposition}\label{itsMu}
  $\CCom(\oc)\left(A\xrightarrow{\Delta}A\times A\right)$ has comultiplication given by $\mu_A\from\oc A \to \oc A\tensor\oc A$ and counit given by the unique morphism $\eta_A\from \oc A \to I$.
\end{proposition}
\begin{proof}
  See appendix.
\end{proof}

In particular, this proves that the comultiplication $\mu_A$ is associative and that the counit $\eta_A$ is a valid counit for $\mu_A$.

We can now state our second main result from this section.

\begin{theorem}
  \label{Coalgebra__CoCoCo}
  Let $(\C,\C_s,J,\wk)$ be a sequoidal category satisfying all the conditions from Theorem \ref{StrongMonoidalFunctor}.  Let $A$ be an object of $\C$ (equivalently, of $\C_s$).  Then $\oc A$, together with the comultiplication $\mu_A$ and counit $\eta_A$, is the cofree commutative comonoid over $A$.
\end{theorem}

\appendix

\section{Proofs}

\subsection{Proof of Proposition \ref{StrongMonoidalFunctorActual}}

\begingroup
\def\thetheorem{\ref{StrongMonoidalFunctorActual}}
\begin{proposition}
  $\sigma\mapsto\oc\sigma$ respects composition, so $\oc$ is a functor.  Moreover, $\oc$ is a strong symmetric monoidal functor from the Cartesian category $(\C, \times, 1)$ to the symmetric monoidal category $(\C, \tensor, I)$, witnessed by $\int$ and $\dec^0$.
\end{proposition}
\addtocounter{theorem}{-1}
\endgroup

@@

@@

\bibliography{bibliography}
